### 2024-07-10 analysis/analysis.qmd
Regression update

### Regression studies

#### Valence: all models, datasets, features

@@

# select regression studies with r2
tmp <- dplyr::filter(metaMER_results,dimension=="valence" & measure=="r2")

# Temporary clarification of N
tmp$stimulus_n[tmp$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 1000
tmp$stimulus_n[tmp$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372
tmp$stimulus_n[tmp$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40
tmp$stimulus_n[tmp$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 818
tmp$stimulus_n <- as.numeric(tmp$stimulus_n)

#sqrt(tmp$values) # convert from R^2 to r
#tmp$stimulus_n <- 100 # ad-hoc for now

m.cor <- metacor(cor = sqrt(values), 
                 n = stimulus_n,
                 studlab = studyREF,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: All")

@@

## Explore qualities

```{r}
meta <- metagen(values, sqrt(values), 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")
find.outliers(meta)
infan <- InfluenceAnalysis(meta)
print(eggers.test(meta))

@@

## Visualise

```{r}
plot(m.cor)
plot(eggers.test(meta))

@@

## Take the max from each study

- Also think of max, median/mean and min?

- Idea: visualise the distributions of the model successes within studies

```{r}
g1 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
  geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
  coord_flip()+
  theme_bw()
g1

@@

## Plot success across the years

```{r}
#| eval: false
g2 <- ggplot(tmp,aes(y=values,fill=model_class_id))+
  geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
  coord_flip()+
  theme_bw()
g2
```

>>>>

## Regression studies

### Valence: Best model

@@

R_studies <- read.csv("R_studies.csv")
R_summary <- read.csv("R_summary.csv")

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp <- dplyr::filter(R_studies,dimension=="valence")
tmp<-drop_na(tmp)
#sqrt(tmp$values) # convert from R^2 to r
#tmp$stimulus_n <- 100 # ad-hoc for now

m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

@@

#### Visualise (forest and funnel plots)

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"),studlab = citekey)
plot(eggers.test(m.cor))
```

#### Explore qualities (in progress)

```{r}
O <- find.outliers(m.cor)
# 6 datasets identified as outliers, without them the r drops to 0.5781
infan <- InfluenceAnalysis(m.cor)
print(eggers.test(m.cor))

```
#### Re-run the analysis without the outliers

```{r}
outliers <- c("chen2017co-various-GMM-mfcc-AMG1608-1", "chen2017co-various-GMM-tonal-AMG1608-1", "chen2017co-various-GMM-spectral-AMG1608-1", "chen2017co-various-GMM-temporal-AMG1608-1", "chen2017co-various-GMM-mfcctonalspectraltemporal-AMG1608-1", "griffiths2021am-various-mlr-mixed-new-validation", "griffiths2021am-various-mlr-mixed-new-validation-nooutliers", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "hu2017cr-various-SVR-mixed-all-1", "koh2023me-openSMILE-fullyconnectedNN-FreeMusicArchive-audioOnly-1", "koh2023me-openSMILE-longshorttermmemoryNN-FreeMusicArchive-audioOnly-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-western-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022co-various-extremelyrandomizedtreeregression-mixed-chinese-1", "wang2022cr-various-pls-mixed-chineseClassicalEnsembles-1", "wang2022cr-various-pls-mixed-chineseClassicalSolo-1", "wang2022cr-various-pls-mixed-westernClassicalEnsembles-1", "wang2022cr-various-pls-mixed-westernClassicalSolo-1", "zhang2019us-marsyas-NuSVR-music-xing2014-1")

tmp2<-tmp[!tmp$unique_id %in% outliers,]
m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id, # unique_id
                 data = tmp2,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 prediction = TRUE,
                 backtransf = TRUE,
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

print(m.cor)

fp <- funnel(m.cor, common = TRUE,studlab=FALSE)

@@

#### Custom funnel plot

To show the quality differences between core and eliminated studies (in progress).

```{r}
tmpdata <- data.frame(SE = m.cor$seTE, Zr = m.cor$TE)
estimate = m.cor$TE.common
se = m.cor$seTE.common
se.seq=seq(0, max(m.cor$cor), 0.001)
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
meanll95 = estimate-(1.96*se)
meanul95 = estimate+(1.96*se)
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

fp = ggplot(aes(x = SE, y = Zr), data = tmpdata) +
  geom_point(shape = 1) +
  xlab('Standard Error') + ylab('Zr')+
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
   geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI) +
#Reverse the x-axis ordering (se) so that the tip of the funnel will appear
#at the top of the figure once we swap the x- and y-axes...
  scale_x_reverse(breaks=seq(0,0.2,0.05),limits=c(0.2,0))+
#Specify the range and interval for the tick-marks of the y-axis (Zr);
#Choose values that work for you based on your data
  scale_y_continuous(breaks=seq(0.3,1.25,0.25),limits=c(0.3,1.25))+
#  scale_x_continuous(breaks=seq(0.2,0,0.05))+
#And now we flip the axes so that SE is on y- and Zr is on x-
  coord_flip()+
#Finally, apply my APA-format theme (see code at end of post).
#You could, alternatively, specify theme_bw() instead.
  theme_bw()

@@

#### Subgroup analysis according to techniques

```{r}
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE,
       prediction = TRUE)

print(m.cor_subgroups)
#forest(m.cor_subgroups,subgroup=TRUE)
```

- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

### Arousal: Best model

```{r}
#| warning: false
#| eval: true

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
m.cor <- metacor(cor = valuesMedian, 
                 n = stimulus_n,
                 studlab = studyREF,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

#### Visualise (forest and funnel plots)

```{r}
forest(m.cor,
       sortvar = TE,
       prediction = FALSE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))
plot(eggers.test(m.cor))
```

#### Explore qualities (in progress)

```{r}
#| eval: false
meta <- metagen(valuesMax, sqrt(valuesMax), 
                data = tmp, 
                studlab = tmp$citekey, 
                comb.fixed = FALSE, 
                method.tau = "PM")
find.outliers(meta)
infan <- InfluenceAnalysis(meta)
print(eggers.test(meta))

#### Subgroup analysis according to techniques

```{r}
update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
       tau.common = FALSE)

forest(m.cor_subgroups,subgroup=TRUE)
```

- Idea: visualise the distributions of the model successes within studies (done in preprocessing)

```{r}
#| eval: false
g1 <- ggplot(tmp,aes(y=valuesMax,fill=model_class_id))+
   geom_histogram(show.legend = T)+
  facet_wrap(.~studyREF)+
   coord_flip()+
   theme_bw()
g1

@@

### 2024-07-10 analysis/preprocessing.qmd
Regression update

@@

g1<-ggplot(R_studies,aes(x=values,fill=citekey))+
             geom_histogram()+
  facet_wrap(.~model_class_id)+
           theme_bw()+
scale_x_continuous(breaks = seq(0,1,by=.1))
           g1
```

>>>>

```
### Homogenise the outcome variable names to valence and arousal

```{r}
R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av')) # relates to distances, can be omitted

table(R_studies$dimension)

table(R_studies$stimulus_n)

# Deal with four studies involving multiple datasets: 
R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 1000, soundtracks: 360, chinese: 500 "] <- 938 #resolved from the paper
R_studies$stimulus_n[R_studies$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372 # resolved
R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40 # decided to take this from validation
# REDO with a clearer function
eliminate <- str_detect(R_studies$unique_id,"hu2017cr") & !str_detect(R_studies$unique_id,"all")
R_studies <- R_studies[!eliminate,]
R_studies$stimulus_n[R_studies$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 60+818+1608 #
R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)

@@

g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
  scale_color_manual(values = c('black','white'))+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

g1
```

### Select a summary measure for valence and arousal separately

```{r}
library(tidyverse)
R_studies$citekey <- factor(R_studies$citekey)
R_studies$dimension <- factor(R_studies$dimension)

R_summary <- summarise(group_by(R_studies,dimension,citekey),valuesMean=mean(values,na.rm=T),valuesMedian=median(values,na.rm=T),valuesMax=max(values,na.rm=T),stimulus_n=first(stimulus_n),studyREF=first(studyREF),model_class_id=first(model_class_id))

### Visualise Summary on two dimensions

Add variation from within the studies (alternative models)

```{r}
R_summary_split <- pivot_wider(R_summary,id_cols = citekey, names_from = c(dimension), values_from = valuesMax)

g2 <- ggplot(R_summary_split,aes(x=valence,y=arousal,label=citekey))+
  geom_label()+
  theme_bw()+
  scale_x_continuous(breaks = seq(0,1,by=.1))+
  scale_y_continuous(breaks = seq(0,1,by=.1))

g2

## could be more informative when done with the full data
R_studies$citekey<-factor(R_studies$citekey)
R_studies$dimension<-factor(R_studies$dimension)

R_studies_split <- pivot_wider(R_studies,id_cols = c(unique_id,citekey,model_class_id), names_from = c(dimension), values_from = c(values),values_fn = mean)
R_studies_split<-drop_na(R_studies_split)

library(ggrepel)

g3 <- ggplot(R_studies_split,aes(x=valence,y=arousal,label=citekey,color=model_class_id,fill=model_class_id))+
  geom_point(size=4)+
  geom_label_repel(size=3, max.overlaps=50,show.legend = T,color='white')+
  scale_x_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
  scale_y_continuous(breaks = seq(0,1,by=.25),limits = c(0,1))+
  theme_bw()
g3

### Plot success across the years

```{r}
#| eval: true
# Add year!
R_studies$year <- as.numeric(str_match(R_studies$citekey,'[0-9]+'))

g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
  geom_point(show.legend = T)+
  facet_wrap(.~dimension)+
  theme_bw()
g3
```
### Simple model complexity metric

Ratio of obs./features or just a classification based on feature n (quintiles).

```{r}
R_studies$feature_n==" 15; 23 in table, but 15 reported "

R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved from the paper

R_studies$feature_n[R_studies$feature_n==" 15; 23 in table, but 15 reported  "] <- 15 #resolved
R_studies$feature_n[R_studies$feature_n==" before_selection = 45, after_selection = 6  "] <- 45 #resolved
R_studies$feature_n[R_studies$feature_n==" model 1: 52, model 2 = 68, model 3 = 260, model 4 = 388 "] <- 388 #resolved
R_studies$feature_n[R_studies$feature_n==" variable, 557 before feature selection "] <- 557 #resolved

R_studies$feature_n[R_studies$feature_n==" 50 PCA features "] <- 50 #resolved
#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved
#R_studies$feature_n[R_studies$feature_n==""] <- 0 #resolved

R_studies$feature_n<-as.numeric(R_studies$feature_n)

print(quantile(R_studies$feature_n,c(0.333,0.666),na.rm = T))
#quantile(R_studies$feature_n,c(0.25,0.50,0.75),na.rm = T)

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 1000),
                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
table(R_studies$feature_n_complexity)
```

### Explore feature_n_complexity and model success

Needs to be done from the unsummarised data (`R_studies`).

```{r}
tmp <- drop_na(R_studies)
library(ggdist)

tmp$dimension<-str_to_title(tmp$dimension)
tmp$model_class_id<-factor(tmp$model_class_id,
                           levels = c("Neural Nets","Flexible Discriminants", "Kernel Smoothing, Additive and KNN", "Random Forests","Linear Methods"),
                           labels = c("Neural\nNets","Flexible\nDiscriminants", "KS\n & KNN", "Random\nForests", "Linear\nMethods"))

g <- ggplot(tmp,aes(x=model_class_id,y=values,color=citekey,label=citekey))+
  stat_halfeye(aes(fill=citekey),point_interval="mean_qi", trim=FALSE, expand=FALSE, show.legend = FALSE,adjust = 1.25, density="bounded", point_size=3,scale = 1,alpha=0.5) + 
  geom_point(alpha=0.5,show.legend = F,position = position_jitter(width = .3))+
  #geom_label_repel(size=2,max.overlaps = 50)+
  facet_wrap(dimension~feature_n_complexity)+
  ylab("Correlation Coefficient")+
  xlab("Model Technique")+
#  scale_y_continuous(limits = c(0,1),expand = c(0.01,0.01))+
  geom_text_repel(aes(x = model_class_id, y = values, label = studyREF),
             stat = "summary", fun = mean,show.legend = F)+
  theme_bw()
g
#ggsave(filename = 'FeatureN_regression.pdf',g,height = 7,width = 11)
```

## Export as csv

```{r}
write.csv(x = R_studies,file = 'R_studies.csv')
write.csv(x = R_summary,file = 'R_summary.csv')
```

### 2024-07-10 manuscript/manuscript.qmd
Regression update

@@

| Concept | N    | Md $R^2$|
|:--------|:-----|:--------|
| Valence | ??   | ??      |
| Arousal | ??   | ??      |

@@

>>>>

- Report all models or the best model?

@@

This is for diagnostic purposes

| Concept     | N,obs     | $r$ 95%-CI              | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:----------|:--------|:--------------|:----|:-----|:-----|:------|
| Valence All | 49,42648  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1% [0.0%; 58.2%]|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
| N Features  |           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| Techniques  |           |                         |     |      |      |       |
|   KS        | 1          | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

| Arousal | 14,9035  | 0.8139 [0.7147; 0.8810] |10.17|.0001 | 0.165| 97.3% |
|   KS    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF    |          | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

model complexity issue

https://ishanjainoffical.medium.com/model-complexity-explained-intuitively-e179e38866b6

https://www.sciencedirect.com/science/article/pii/S0925231220317525

bake in number of features, + N + success
AIC =
